Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-06 paper.tex
edit README.md

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a tool that
is used to make applications reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
\tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. Its alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

>>>>

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
helps scientists to make their research reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
\tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. Its alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.
